True versus apparent shapes of astrophysical bow shocks

### 2017-03-28 papers/Paper1/sec-quadrics-observations.tex
Finish Figure 19 and caption: Rc-R90 plane for OB bow shocks

\begin{figure*}
  \centering
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom} &
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
  \end{tabular}
  \caption[]{MIPSGAL sources on the bow shock shape diagnostic
    diagram.  (a) Individual sources.  (b) Kernel density estimate of
    the distribution.}
  \label{fig:mipsgal-shapes}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom-annotated} &
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
  \end{tabular}
  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
    of dimensionless radius of curvature versus perpendicular radius.
    (a) Individual sources with bow shock fit quality rating of 3-star
    or above.  All 5-star sources plus those 4-star sources with
    \(R_c/R_0 < 1\) are labelled with their \cite{Kobulnicky:2016a}
    catalog number.  Horizontal error bars do not directly reflect the
    uncertainty in \(R_c/R_0\) but are instead simply the standard
    deviation from the circle fit of bowshock points \(R_k\) within
    \(\pm 45\degr\) of the axis.  Values on the vertical axis
    represent the average of \(R_{90+}\) and \(R_{90-}\), with thin
    vertical error bars showing the difference between \(R_{90+}\) and
    \(R_{90-}\), and thick vertical error bars showing the rms
    dispersion of \(R_k\) about these values for bow shock points
    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
    directions.  (b) Kernel density estimate of the distribution for
    3-star sources (blue, filled contours) and 4- plus 5-star sources
    (orange/brown, unfilled contours).  Images of representative 4-
    and 5-star sources at different points on the \(R_c\)--\(R_{90}\)
    plane are also shown.}
  \label{fig:mipsgal-shapes}
\end{figure*}
